---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# travispkg

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mbojan/travispkg.svg?branch=master)](https://travis-ci.org/mbojan/travispkg)
<!-- badges: end -->

This is a proof-of-concept dummy R package that aims to use TravisCI to:

- Run `R CMD check` on Linux, MacOS, and **Windows**.
- Push package tarball, MacOS binary, and Windows binary to a [drat](https://github.com/eddelbuettel/drat) repository, as proposed [here](https://cran.r-project.org/web/packages/drat/vignettes/CombiningDratAndTravis.html)

To that end the `.travis.yml` runs script files kept in `.travis` folder.

Built packages are pushed to drat repository at <https://mbojan.github.io/drat> and can be inspected with

```{r}
available.packages(repos="https://mbojan.github.io/drat")
available.packages(repos="https://mbojan.github.io/drat", type="win.binary")
```

and installed with by using [drat](dirk.eddelbuettel.com/code/drat.html) facilities as described [here](http://eddelbuettel.github.io/drat/DratForPackageUsers.html):

```{r, eval=FALSE}
drat::addRepo("mbojan")
install.packages("travispkg")
```

or simply:

```{r, eval=FALSE}
install.packages("travispkg", repos="https://mbojan.github.io/drat")
```

